---
title: "Team Project Group 18"
output: 
 html_document:
  toc: true
  toc_depth: 3
  theme: lumen
  code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Group Names
Reed Baumgardner
Nathan Patton
Fadumo Hussein

# Topic
NFL Injuries

# Possible Data Sources
[Kaggle-- NFL Injury Analysis](https://www.kaggle.com/code/aleksandradeis/nfl-injury-analysis/data)

# Possible Questions
What variables correlate positively with NFL injuries? (injury surface, weather, stadium type, position, etc)

Is it more common to get injured in the cold/rain? Indoor/Outdoor stadiums?

Which variables are causing the most severe injuries (measured by days out)?

Which position is most at risk? In which conditions?

Analysis per position. Which variables are linked to the most QB injuries?

#Packages 
```{r}
library(tidyverse)
library(ggplot2)
library(mice)
```

#Uplaod Data 
```{r}
InjuryRecord <- read.csv("InjuryRecord.csv")
View(InjuryRecord)
PlayList <- read.csv("PlayList.csv")
View(PlayList)
```

#Checking for missing values and cleaning up data 
```{r}
#Checking for missing values injury record 
InjuryRecord[InjuryRecord==""] <- NA
colSums(is.na(InjuryRecord))
md.pattern(InjuryRecord, rotate.names = TRUE)
str(InjuryRecord)

#Checking for missing values playlist 
PlayList[PlayList==""] <- NA
colSums(is.na(PlayList))
md.pattern(PlayList, rotate.names = TRUE)
str(PlayList)
```

#Rename columns and merging table 
```{r}
injuries <- inner_join(PlayList, InjuryRecord, by="PlayKey")
injuries <- select(injuries, -c("PlayerKey.y","GameID.y","Surface"))
injuries <- injuries %>%
  rename("PlayerKey" = "PlayerKey.x", "GameID" = "GameID.x")
View(injuries)
```















